% IMPORTS
\documentclass{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{multicol}

% CONFIGURATIONS
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=cyan
}  % https://www.overleaf.com/learn/latex/hyperlinks
\pagenumbering{gobble}

% COMMANDS
\newcommand{\side}[1]{\hspace*{\fill}#1} 			% For date information
\newcommand{\tab}{\hspace*{4mm}} 			% Indent
\newcommand{\header}[1]{\section*{\underline{#1}}}	% Header
\newcommand{\bb}[1]{\textbf{#1}} 				% Emphasis lvl 1
\newcommand{\bi}[1]{\textbf{\textit{#1}}} 			% Emphasis lvl 2
\newcommand{\ii}[1]{\textit{#1}} 				% Emphasis lvl 3

% DOCUMENT
\begin{document}
\begin{center}


\section*{Cody Perakslis}
\url{https://codyperakslis.com}, 
\href{mailto:perak005@umn.edu}{perak005@umn.edu}\\
\end{center}
\begin{multicols}{2}


\header{Education} % Education
\bb{University of Minnesota-TC Graduate}, grad 05/2021\\
\tab \bi{M.S. Computer Science}\\
\bb{University of Minnesota-TC Undergrad}, grad 05/2020\\
\tab \bi{B.S. Computer Science}\\
\tab \tab \bi{Philosophy Major} \\
\tab \tab \bi{Mathematics Major}\\
\tab \ii{Honor's Program}\\
\tab \href{https://github.com/CodyPerakslis/resume/blob/master/SSR_TSRPT.pdf}{GPA: 3.894}
\columnbreak


\header{Skills}
\bb{Major Skill Area}\\
Cloud Backend in AWS\\
\bb{Major Languages}\\
Python, Golang, C/C++, Swift\\
\bb{CI/CD}\\
Docker, Ansible, Git, Jenkins, SonarQube, Agile Method\\
\bb{See More}\\
Checkout out my Github \href{https://github.com/CodyPerakslis}{github.com/CodyPerakslis} 
\end{multicols}


\header{Work Experiences}
\bb{Edge Computing Research}, Minneapolis, MN \side{05/2019 - Present.}\\
\tab Work in the Distributed Computing Research Group in designing a docker-based \\
decentralized edge computing (cloud computing but with smaller volunteer machines)\\ 
system, called Armada, built using Golang.\\
\\
\bb{Co-Founder of The Voy App}, Minneapolis, MN \side{01/2018 - 12/2019}\\
\tab I am the technical co-founder of this audio-touring platform. We have the locations \\
in a POSTGIS database hosted out of AWS to populate audio geofences in apps for \\
iOS. Most of my development is focused on backend. I manage the programming effort \\
and finances and org structure. \url{https://www.thevoyapp.com}\\
\\
\bb{Cloud Automation Intern at SPS Commerce}, Minneapolis, MN \side{05/2017 - 08/2018}\\
\tab I worked with the cloud automation/security \& compliance teams. I wrote a system \\
to run generic tasks on a shared AWS ECS Cluster. Later refactored the code and \\
updated the API (backwards compatibly). I set up a containerized deployment model \\
for Ansible run on Jenkins. I set up the database and server for SonarQube and helped\\
give a talk on why to use it and demo on how to use it.\\
\\
\bb{Csci 2021: Machine Architecture TA at UMN}, Minneapolis, MN \side{01/2018 - 05/2018}\\
\bb{Summer IT Assistant at Yankton School District}, Yankton, SD \side{Summers 05/2014 - 08/2016}


\header{Technical Experiences}
\bb{President and Founder of the Cloud Computing Student Group} \side{11/2017 - 12/2019}\\
\tab I want to teach others the power of the cloud. \url{https://www.umncloud.com}
\\
\bb{Hackathon} \side{10/2018, 01/2020}\\
\tab \href{https://devpost.com/software/surround-7fyc9t}{Surround} App at HackHarvard 2018. \href{https://devpost.com/software/socialize}{Social Capital} App at Minnehack 2020. 
\\
\bb{Self-Selected Class Projects} \side{05/2018} \\
\tab Sentiment Analysis for Intro AI, VM Handoff in OpenStack++ for Dispersed Computing\\ 
\tab Chatbot for Senior Software Proj, Cross-Platform App Comparison for Mobile Computing
\\
\bb{Coding Club Guru Volunteer} \side {2015 - 2016}\\
\tab I helped teach Scratch programming to elementary students. Ran after the instructor quit. 

\header{Unique Experiences}
\bb{President of Philosophy Club} \side{04/2018 - Present.}\\
\tab We have a member (usually an officer) present on a topic, then have group discussion.
\\
\bb{President of Tau Beta Pi} \side{09/2019 - Present.}\\
\tab An engineering honor society with a chapter on campus. I have been a member since 01/2018.
\\
\bb{Writer for The Wake Magazine} \side{09/2016 - 10/2018}\\
\tab I frequently wrote opinion pieces in the realm of technology or global policy.
\\
\end{document}

